Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.tex
smoothing edits

\begin{abstract}
The ability to process social cues--including eye gaze--is a critical
component of children's early language and cognitive development.
However, as children reach their first birthday, they begin to locomote
themselves, walking and exploring their visual environment in an
entirely new way. How do these postural and locomotive changes affect
children's access to the social information relevant for word-learning?
Here, we explore this question by using head-mounted cameras to record
infants' (8-16 months of age) egocentric visual perspective and use
computer vision algorithms to detect the proportion of faces and hands
in infants' environments. We find that infants' posture and orientation
to their caregiver largely mediate infants' access to socially
informative features, suggesting that postural and locomotive
developments play a significant role in the emergence of children's
linguistic and social capacities. Broadly, we suggest that the combined
use of head-mounted cameras and the application of new computer vision
techniques is a promising avenue for understanding the statistics of
infants' visual and linguistic experience.

@@

Children are deeply engaged in learning from others (Csibra \& Gergely,
2009; Meltzoff, 2007) and attend to the social information in their
environment from their earliest days. Even newborns tend to prefer to
look at faces with direct vs.~averted gaze (Farroni, Csibra, Simion, \&
Johnson, 2002) and follow overt gaze shifts by 6 months of age
(Gredebäck, Fikke, \& Melinder, 2010; Gredebäck, Theuring, Hauf, \&
Kenward, 2008). And when infants free-view videos, they tend to look
mostly at faces at the expense of other visual information--though older
infants start to look towards people's hands and the actions they are
performing (Frank, Amso, \& Johnson, 2014; Frank, Vul, \& Saxe, 2012).

However, as children are learning from others around them, their view of
the world is also changing radically (K. Adolph \& Berger, 2007).
Infants' motor abilities improve dramatically near the end of the first
year of life, allowing them to locomote independently. These motor
changes have drastic consequences for what children see; crawling and
walking infants have radically different views of the world. For
example, during spontaneous play in a laboratory playroom, toddlers are
more likely to look at the floor while crawling than while walking (J.
Franchak, Kretch, Soska, \& Adolph, 2011); in general, walking infants
tend to have full visual access to their environment and the people in
it, while crawling infants do not (K. S. Kretch, Franchak, \& Adolph,
2014).

One possibility is that these motor improvements have strong
developmental cascades, impacting children's emerging social, cognitive,
and linguistic abilities (Iverson, 2010). Indeed, these postural changes
also impact how children interact with their mothers; walking
(vs.~crawling) infants make different kinds of object-related bids for
attention from their mothers and tend to hear more action directed
statements (e.g., ``open it'') (Karasik, Tamis-LeMonda, \& Adolph,
2014). Further, in an observational study, Walle \& Campos (2014) found
that children who were able to walk had both higher receptive and
productive vocabularies. On their account, children's ability to stand
and independently locomote may fundamentally change their ability to
access social information (e.g., faces, gaze) relative to children who
are still crawling and sitting. In other words, the ability to walk and
move around independently and subsequently access more detailed social
information may accelerate infants' ability to learn from the people in
their environments.

Recent technological developments allow for testing of this hypothesis
by documenting the experiences of infants and children from their own
perspective. By using head-mounted cameras, researchers have begun to
document visual experiences of infants and children --- which even for
walking children are radically different from the adult perspective (and
not easily predicted by our own adult intuitions) (Clerkin, Hart, Rehg,
Yu, \& Smith, 2017; J. Franchak et al., 2011; Yoshida \& Smith, 2008).
Children's views tend to be restricted and to be dominated by objects
and hands much more than that of adults (Yoshida \& Smith, 2008), and
both computational and empirical work suggest that this restricted
viewpoint may be more effective for learning objects and their labels
than the comparable adult perspective (Bambach, Crandall, Smith, \& Yu,
2017; D. Yurovsky, Smith, \& Yu, in press). Further, recent work also
suggests dramatic changes in the child's perspective over the first two
years of life, as views transition from primarily containing a close up
view of faces to capturing views of hands paired with the objects they
are acting on (Fausey, Jayaraman, \& Smith, 2016).

Here, we directly ask whether postural and locomotive developments
change the availability of social information--the presence of faces and
hands. To do so, we recorded the visual experience of a group of infants
in three age ranges (8,12, and 16 months) using head-mounted cameras
during a brief laboratory free-play session; children's posture and
orientation relative to their caregiver were also recorded from a
third-person perspective and hand-annotated. We then capitalize on
recent improvements in face and pose detection algorithms (Cao, Simon,
Wei, \& Sheikh, 2017; K. Zhang, Zhang, Li, \& Qiao, 2016) to analyze the
frequencies of faces and hands (using wrists as a proxy for the latter)
in the child's visual environment, both overall and relative to naming
events by their caregivers. We hypothesized that there would be
differential access to social information based on children's postural
developments: crawling infants would see fewer faces because they would
primarily be looking at the ground, while walking toddlers would have
access to a richer visual landscape thus enabling a larger portion of
the social information in their environment to be accessible.

that would contain a larger portion of the social information in the
environment.

@@

Even with the fish-eye lens, the vertical field of view of the camera is
still considerably reduced compared to the child's approximate vertical
field of view, which spans around 100--120\(^{\circ}\) in the vertical
dimension by 6-7 months of age (Cummings, Van Hof-Van Duin, Mayer,
Hansen, \& Fulton, 1988; Mayer, Fulton, \& Cummings, 1988). As we were
primarily interested in the presence of faces in the child's field of
view, we chose to orient the camera upwards to capture the entirety of
the child's upper visual field where the child is likely to see the
faces of adults around them. This choice allowed us to maximize our
chances of capturing faces that the child would have seen during the
play session.

@@

First, all parents signed consent documents in a waiting room where
children were fitted with the headcam. After the child was comfortable
in the waiting room and with the experimenter, the experimenter placed
the headcam on the child's head. If the child was uninterested in
wearing the headcam or tried to take it off, the experimenter presented
engaging toys to try to draw the child's focus away from the headcam
(Yoshida \& Smith, 2008).

After the child was comfortable wearing the headcam, the child and
caregiver were shown to a playroom for the free-play session--the focus
of the current study. Parents were shown a box containing three pairs of
novel and familiar objects (e.g., a ball and a microfiber duster, named
a ``zem''), and were instructed to play with the object pairs with their
child one at a time, ``as they typically would.'' All parents confirmed
that their child had not previously seen the novel toys and were
instructed to use the novel labels to refer to the novel toys.

The experimenter then left the playroom for approximately 15 minutes,
during which a tripod-mounted camera in the corner of the room recorded
the session and the headcam captured video from the child's perspective.

@@

We used three face detection systems to explore infants' changing access
to social information and to avoid the cost of hand-annotating every
frame. The first of these is the most commonly-used and widely available
face detection algorithm: Viola-Jones. We used this as a benchmark for
performance; while it can achieve impressive accuracy in some
situations, it is notoriously bad at dealing with occluded faces
(Scheirer, Anthony, Nakayama, \& Cox, 2014). We next capitalized on
recent improvements in computer vision, testing the performance of two
face detectors that both made use of Convolutional Neural Networks
(CNNs) to extract face information. The first algorithm was specifically
optimized for face detection, and the second algorithm was optimized to
extract information about the position of 18 different body parts
belonging to an agent.

This second of the CNN-based algorithms--the pose detector--provided us
with the location of an agent's wrists, which we used as a proxy for the
presence of a hand. We did so first because we did not capture the
entire visual field experienced by the infants/children. Thus, even
though the video may only show the presence of a wrist, the caregiver's
hand may be within the child's field of view. Second, we did so because
hands are often occluded by objects when caregivers are interacting with
children, yet still visually accessible by the child and part of their
joint interaction. For example, if a caregiver was holding a toy and
presenting it to the infant, their wrists may be visible but their hand
may not necessarily be (as it is occluded by the toy). Similarly, we
used an agent's nose (one of the 18 body parts detected) to
operationalize face presence, as any half of a face necessarily contains
a nose.

@@

The first face detection system made use of a series of Haar
feature-based cascade classifiers (Viola \& Jones, 2004) applied to each
individual frame. This detector provided information about the presence
of a face as well as its size and position.

The second algorithm was based on the work by K. Zhang et al. (2016)
using multi-task cascaded convolutional neural networks (MTCNNs). The
system was built using a novel cascaded CNN-based framework for joint
detection and alignment, built to perform well in real-world
environments where varying illuminations and occlusions are present. We
used a Tensorflow implementation of this algorithm provided by
(\url{https://github.com/davidsandberg/facenet}). Like Viola-Jones, this
detector provided information about the presence of a face as well as
its size and position.

The third algorithm was a CNN-based pose detector that provided the
locations of 18 body parts (ears, nose, wrists, etc.) called OpenPose
(Cao et al., 2017; Simon, Joo, Matthews, \& Sheikh, 2017; Wei,
Ramakrishna, Kanade, \& Sheikh, 2016) avaliable at
\url{https://github.com/CMU-Perceptual-Computing-Lab/openpose}. The
system uses a CNN for initial anatomical detection and subsequently
applies part affinity fields (PAFs) for part association, producing a
series of body part candidates. The candidates are then matched to a
single individual and finally assembled into a pose. For the purposes of
our investigation we only made use of the body parts relevant to the
face and hands (nose and wrists). We operationalized face detections as
any frames containing a nose, and hand detections as any frames
containing either the left or the right wrist.

@@

To evaluate face detector performance, we needed to construct an
unbiased ``gold set'' of labeled frames that made sure to account for
the relatively rare appearance of faces in the dataset. We thus
hand-labeled two samples: a sample containing a high density of faces
(half reported by MTCNN, half by OpenPose) and a random sample from the
remaining frames. Each sample was comprised of an equal number of frames
taken from each participant (i.e., video). Faces were classifed as
present in a frame if at least half of the face was showing. Precision
(hits / hits + false alarms), recall (hits / hits + misses), and F-score
(harmonic mean of precision and recall) were calculated for all
detectors and are reported in Table 2. For wrist detections, the ``gold
set'' was constructed in the same manner, with the exception that frames
with a high density of wrists were taken by pose detections made by
OpenPose.

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose); thus the face
presence analyses to follow all result from MTCNN detections. We found
that although MTCNN and OpenPose perform comparably with the random
sample, MTCNN performed better on the high density sample (specifically
looking at precision), suggesting that OpenPose generated more false
positives than MTCNN. ViolaJones performed quite poorly relative to the
other detectors especially with respect to the random sample.

@@

First, we report developmental shifts in infants' posture and their
orientation relative to their caregiver. Then, we explore how these
changes influence children's visual access to faces and hands across
this developmental time range. Finally, we explore how these changes
impact the accessibility of faces and hands during labeling events.

@@

\caption[Proportion of faces detected by the MTCNN model (left) and wrists detected by the OpenPose model (right) as a function of child's age]{Proportion of faces detected by the MTCNN model (left) and wrists detected by the OpenPose model (right) as a function of child's age. Larger dots indicate children who had longer play sessions and thus for whom there was more data.}\label{fig:detByAge}
\end{figure}
\end{CodeChunk}

However, we found that any age related effects were much smaller
compared to the impact of postural and locomotive changes on children's
visual access to faces. Children's posture was a major factor both in
how many faces they saw during the play session. Infants who were
sitting saw more faces than infants who were lying down or being
carried, while infants who were standing saw the most faces. We also
examined how the child's orientation relative to their caregiver
impacted their visual access to faces: children who were far away from
their caregiver were more likely to see faces than children who were
close to their caregiver; this was true within all age groups and for
both face detectors.

\begin{CodeChunk}
\begin{figure*}[h]

@@

To formalize these observations, we fit a generalized linear model to
the proportion of faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p = 0.89). We found the same pattern of results
for the OpenPose face detections, omitted here for brevity. We also
found the same pattern with respect to infant's visual access to hands
(see Table 4); including interaction terms also eliminated any main
effect of age on the proportion of hands detected (b = -15.7, SE =
113.98, z = -0.14, p = 0.89). Thus, these results suggest that infants'
access to social information is heavily influenced by their postural and
locomotive development.

@@

Finally, we analyzed how face and wrist detections changed during object
labeling events as a function of infant's posture and orientation.
Specfically, we analyzed a four-second window around each labeling event
(e.g., ``Look at the {[}zem{]}!''); these labeling events were
hand-annotated and automatically synchronized with the frame-by-frame
face detections. We found that infants' posture and orientations
impacted the degree to which they saw their caregiver's face and wrist
during a labeling event; infants who were sitting or standing were more
likely to have access to this social information. However, this did not
manifest in a direct change the presence of wrists/hands before
vs.~after naming events (average difference in proportion of wrists
detected, 8 m.o. = -0.006, 12 m.o. = -0.013, 16 m.o. = -0.007) or in
proportion of faces detected (average difference in proportion of faces
detected, 8 m.o. = -0.002, 12 m.o. = 0, 16 m.o. = -0.004).

@@

We used a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and hands that were available in the child's visual field. Thus,
infants' postural and locomotive developments are mediating factors that
explain some of the age-related changes in the proportion of faces and
wrists/hands that are visually available to infants. Broadly, this work
suggests that motoric developments mediate how infants experience their
visual world and the social information in it: infants that are sitting
and standing have a different view of their world, the people in it, and
the actions that are being performed.

>>>>

\begin{abstract}
The ability to process social cues--including eye gaze--is a critical
component of children's early language and cognitive development.
However, as children reach their first birthday, they begin to locomote
themselves, walking and exploring their visual environment in an
entirely new way. How do these postural and locomotive changes affect
children's access to the social information relevant for word-learning?
Here, we explore this question by using head-mounted cameras to record
infants' (8-16 months of age) egocentric visual perspective and use
computer vision algorithms to detect the proportion of faces and wrists
in infants' environments. We find that infants' posture and orientation
to their caregiver largely mediates their access to social information,
suggesting that postural and locomotive developments play a significant
role in the emergence of children's linguistic and social capacities.
Broadly, we suggest that the combined use of head-mounted cameras and
the application of new computer vision techniques is a promising avenue
for understanding the statistics of infants' visual and linguistic
experience.

@@

Children are deeply engaged in learning from others (Csibra \& Gergely,
2009; Meltzoff, 2007) and attend to the social information in their
environment from their earliest days. Even newborns tend to prefer to
look at faces with direct vs.~averted gaze (Farroni, Csibra, Simion, \&
Johnson, 2002) and young infants follow overt gaze shifts (Gredebäck,
Fikke, \& Melinder, 2010; Gredebäck, Theuring, Hauf, \& Kenward, 2008).
Further, when infants free-view videos, they tend to look mostly at
faces at the expense of other visual information--though older infants
start to look towards people's hands and the actions they are performing
(Frank, Amso, \& Johnson, 2014; Frank, Vul, \& Saxe, 2012).

However, as children are learning from others around them, their view of
the world is also radically changing (K. Adolph \& Berger, 2007).
Infants' motor abilities improve dramatically near the end of the first
year of life, allowing them to locomote independently. These motor
changes have significant consequences for what children see; crawling
and walking infants simply have different views of the world. For
example, during spontaneous play in a laboratory playroom, toddlers are
more likely to look at the floor while crawling than while walking (J.
Franchak, Kretch, Soska, \& Adolph, 2011); in general, walking infants
tend to have full visual access to their environment and the people in
it, while crawling infants do not (K. S. Kretch, Franchak, \& Adolph,
2014).

One possibility is that these motor improvements have strong
developmental cascades, impacting children's emerging social, cognitive,
and linguistic abilities (Iverson, 2010). Indeed, these postural changes
also impact how children interact with their mothers; walking
(vs.~crawling) infants make different kinds of object-related bids for
attention from their mothers and tend to hear more action directed
statements (e.g., ``open it'') (Karasik, Tamis-LeMonda, \& Adolph,
2014). Further, in an observational study, Walle \& Campos (2014) found
that children who were able to walk had both higher receptive and
productive vocabularies. On their account, children's ability to stand
and independently locomote may fundamentally change their ability to
access social information (e.g., faces, gaze) and in turn to accelerate
their own learning.

Recent technological developments allow for testing of this hypothesis
by documenting the experiences of infants and children from their own
perspective. By using head-mounted cameras, researchers have begun to
record the visual experiences of infants and children-- which even for
walking children are extremely different from the adult perspective (and
not easily predicted by our own adult intuitions) (Clerkin, Hart, Rehg,
Yu, \& Smith, 2017; J. Franchak et al., 2011; Yoshida \& Smith, 2008).
While children's views tend to be more restricted and dominated by
objects and hands (Yoshida \& Smith, 2008), both computational and
empirical work suggest that this restricted viewpoint may be more
effective for learning objects and their labels than the comparable
adult perspective (Bambach, Crandall, Smith, \& Yu, 2017; D. Yurovsky,
Smith, \& Yu, in press). Further, recent work also suggests dramatic
changes in the child's perspective over the first two years of life, as
views transition from primarily containing close up views of faces to
capturing views of hands paired with the objects they are acting on
(Fausey, Jayaraman, \& Smith, 2016).

Here, we directly examine whether postural and locomotive developments
change the availability of social information--the presence of faces and
hands. To do so, we recorded the visual experience of a group of infants
in three age ranges (8,12, and 16 months) using head-mounted cameras
during a brief laboratory free-play session; children's posture and
orientation relative to their caregiver were also recorded from a
third-person perspective and hand-annotated. We then capitalize on
recent improvements in face and pose detection algorithms (Cao, Simon,
Wei, \& Sheikh, 2017; K. Zhang, Zhang, Li, \& Qiao, 2016) to analyze the
frequencies of faces and hands (using wrists as a proxy for the latter)
in the child's visual environment, both overall and relative to naming
events by their caregivers. We hypothesized that there would be
differential access to social information based on children's postural
developments: crawling infants would see fewer faces because they would
primarily be looking at the ground, while walking toddlers would have
access to a richer visual landscape, thus rendering accessible a larger
portion of the social information in their environment.

@@

Even with the fish-eye lens, the vertical field of view of the camera is
still considerably reduced compared to the child's approximate vertical
field of view, which spans around 100--120\(^{\circ}\) in the vertical
dimension by 6-7 months of age (Cummings, Van Hof-Van Duin, Mayer,
Hansen, \& Fulton, 1988; Mayer, Fulton, \& Cummings, 1988). As we were
primarily interested in the presence of faces in the child's field of
view, we chose to orient the camera upwards to capture the entirety of
the child's upper visual field where the child is likely to see adult
faces.

@@

First, all parents signed consent documents in a waiting room where
children were fitted with the headcam. After the child was comfortable
in the waiting room and with the experimenter, the experimenter placed
the headcam on the child's head. If the child was uninterested in
wearing the headcam or tried to take it off, the experimenter presented
engaging toys to try to draw the child's focus away from the headcam
(Yoshida \& Smith, 2008). After the child was comfortable wearing the
headcam, the child and caregiver were shown to a playroom for the
free-play session. Parents were shown a box containing three pairs of
novel and familiar objects (e.g., a ball and a microfiber duster, named
a ``zem''), and were instructed to play with the object pairs with their
child one at a time, ``as they typically would.'' All parents confirmed
that their child had not previously seen the novel toys and were
instructed to use the novel labels to refer to the novel toys. The
experimenter then left the playroom for approximately 15 minutes, during
which a tripod-mounted camera in the corner of the room recorded the
session and the headcam captured video from the child's perspective.

@@

We used three face detection systems to measure infants' changing access
to faces. The first of these is the most commonly-used and widely
available face detection algorithm: Viola-Jones. We used this as a
benchmark for performance, as while it can achieve impressive accuracy
in some situations, it is notoriously bad at dealing with occluded faces
(Scheirer, Anthony, Nakayama, \& Cox, 2014). We next capitalized tested
the performance of two face detectors that both made use of recently
developed Convolutional Neural Networks (CNNs) to extract face
information. The first algorithm was specifically optimized for face
detection, and the second algorithm was this to extract information
about the position of 18 different body parts. For the second algorithm
(called OpenPose) (Cao et al., 2017), we used the agent's nose (one of
the 18 body parts detected) to operationalize the presence of faces, as
any half of a face necessarily contains a nose.

The OpenPose detector also provided us with the location of an agent's
wrists, which we used as a proxy for the presence of a hand. We did so
first because we did not capture the entire visual field experienced by
the infants/children. Thus, even though the video may only show the
presence of a wrist, the caregiver's hand may be within the child's
field of view. Second, we did so because hands are often occluded by
objects when caregivers are interacting with children, yet still
visually accessible by the child and part of their joint interaction.
For example, if a caregiver was holding a toy and presenting it to the
infant, their wrists may be visible but their hand may not necessarily
be (as it is occluded by the toy).

@@

The first face detection system made use of a series of Haar
feature-based cascade classifiers (Viola \& Jones, 2004) applied to each
individual frame. This detector provided information about the presence
of a face as well as its size and position. The second algorithm (based
on work by K. Zhang et al. (2016)) using multi-task cascaded
convolutional neural networks (MTCNNs). The system was built using a
novel cascaded CNN-based framework for joint detection and alignment,
built to perform well in real-world environments where varying
illuminations and occlusions are present. We used a Tensorflow
implementation of this algorithm provided by
(\url{https://github.com/davidsandberg/facenet}). Like Viola-Jones, this
detector provided information about the presence of a face as well as
its size and position.

The CNN-based pose detector (OpenPose (Cao et al., 2017; Simon, Joo,
Matthews, \& Sheikh, 2017; Wei, Ramakrishna, Kanade, \& Sheikh, 2016))
provided the locations of 18 body parts (ears, nose, wrists, etc.)
avaliable at
\url{https://github.com/CMU-Perceptual-Computing-Lab/openpose}. The
system uses a CNN for initial anatomical detection and subsequently
applies part affinity fields (PAFs) for part association, producing a
series of body part candidates. The candidates are then matched to a
single individual and finally assembled into a pose; here, we only made
use of the body parts relevant to the face and hands (nose and wrists).
We operationalized face detections as any frames containing a nose, and
hand detections as any frames containing either the left orright wrist.

@@

To evaluate face detector performance, we constructed an unbiased ``gold
set'' of labeled frames that accounted for the relatively rare
appearance of faces in the dataset. We thus hand-labeled two samples: a
sample containing a high density of faces (half reported by MTCNN, half
by OpenPose) and a random sample from the remaining frames. Each sample
was comprised of an equal number of frames taken from each child's
video. Faces were classifed as present in a frame if at least half of
the face was showing. Precision (hits / hits + false alarms), recall
(hits / hits + misses), and F-score (harmonic mean of precision and
recall) were calculated for all detectors and are reported in Table 2.
For wrist detections, the ``gold set'' was constructed in the same
manner, with the exception that frames with a high density of wrists
were taken by pose detections made by OpenPose.

For face detection, MTCNN outperformed OpenPose when taking into account
only the composite F-score (0.89 MTCNN vs.~0.83 OpenPose); we thus use
MTCNN detections in the following analyses. Although MTCNN and OpenPose
performed comparably with the random sample, MTCNN performed better on
the high density sample (specifically looking at precision), suggesting
that OpenPose generated more false positives than MTCNN. ViolaJones
performed quite poorly relative to the other detectors, especially with
respect to the random sample.

@@

First, we report developmental shifts in infants' posture and their
orientation relative to their caregiver. Then, we explore how these
changes influence children's visual access to faces and wrists/hands
across this developmental time range. Finally, we explore how these
changes impact the accessibility of faces and wrists/hands during
labeling events.

@@

\caption[Proportion of faces detected by the MTCNN model (left) and wrists detected by the OpenPose model (right) as a function of child's age]{Proportion of faces detected by the MTCNN model (left) and wrists detected by the OpenPose model (right) as a function of child's age. Larger dots indicate children who had longer play sessions and thus for whom there was more data.}\label{fig:detByAge}
\end{figure}
\end{CodeChunk}\begin{CodeChunk}
\begin{figure*}[h]

@@

To formalize these observations, we fit a generalized linear model to
the proportion of faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p = 0.89). We also found the same pattern with
respect to infant's visual access to hands (see Table 4); including
interaction terms also eliminated any main effect of age on the
proportion of hands detected (b = -15.7, SE = 113.98, z = -0.14, p =
0.89). Thus, these results suggest that infants' access to social
information is heavily influenced by their postural and locomotive
developments.

@@

Finally, we analyzed how face and wrist/hand detections changed during
object labeling events as a function of infant's posture and
orientation. Specfically, we analyzed a four-second window around each
labeling event (e.g., ``Look at the {[}zem{]}!''); these labeling events
were hand-annotated and automatically synchronized with the
frame-by-frame face detections. We found that infants' posture and
orientations impacted the degree to which they saw their caregiver's
face and wrist during a labeling event; infants who were sitting or
standing were more likely to have access to this social information.
However, this did not manifest in a direct change the presence of
wrists/hands before vs.~after naming events (average difference in
proportion of wrists detected, 8 m.o. = -0.006, 12 m.o. = -0.013, 16
m.o. = -0.007) or in proportion of faces detected (average difference in
proportion of faces detected, 8 m.o. = -0.002, 12 m.o. = 0, 16 m.o. =
-0.004).

@@

We used a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and wrists/hands that were available in the child's visual field.
Thus, infants' postural and locomotive developments are mediating
factors that explain some of the age-related changes in the proportion
of faces and wrists/hands that are visually available to infants.
Broadly, this work suggests that motoric developments mediate how
infants experience their visual world and the social information in it:
infants that are sitting and standing have a different view of their
world, the people in it, and the actions that are being performed.
